### 2016-10-10 doc/chap-3-refman.tex
Added the HTML debugger

If \verb!-cfgBuilder:dot=dot! is given,
\safe writes the resulting CFG in a graph visualization format
to file names \verb!dot.gv! and \verb!dot.pdf!.

\item \verb!analyze -analyzer:silent!\\
\hspace*{4.4em}\verb!-analyzer:out={out}!\\
\hspace*{4.4em}\verb!-analyzer:console!

@@

If \verb!-analyzer:console! is given,
\safe enables a user to debug analysis results by navigating the intermediate
status of the analysis.
We describe this facility in the next section.

@@

\medskip\noindent
\fbox{\texttt{print cfg}}\\[.2em]
It prints the current CFG as an input file to the \verb!dot! program.

>>>>

If \verb!-cfgBuilder:dot=name! is given,
\safe writes the resulting CFG in a graph visualization format
to file names \verb!name.gv! and \verb!name.pdf!.

\item \verb!analyze -analyzer:silent!\\
\hspace*{4.4em}\verb!-analyzer:out={out}!\\
\hspace*{4.4em}\verb!-analyzer:console!\\
\hspace*{4.4em}\verb!-analyzer:html={html}!

@@

If \verb!-analyzer:console! is given,
\safe enables a user to debug analysis results by investigating the intermediate
status of the analysis.

If \verb!-analyzer:html=name! is given,
\safe writes the resulting CFG with states that can be investigated to
file name \verb!name.html!.

We describe these facilities in the next section.

@@

\medskip\noindent
\fbox{\texttt{print cfg}}\\[.2em]
It prints the current CFG to files \verb!cfg.gv! and \verb!cfg.pdf!.

\medskip\noindent
\fbox{\texttt{print html}}\\[.2em]
It prints the current CFG and its state to the \verb!cfg.html! file.
We describe this facility in the next section.

\subsection{Analyzer debugging with browsing}
\label{s:3:2:2:refman}
The \verb!print html! command writes the current status into an HTML file
so that a user can investigate the analysis status from a browser.
Consider the following snapshot:
\begin{figure}[H]
\includegraphics[width=8.75cm]{htmldebugger.png}
\end{figure}
\noindent
which shows the current CFG in the middle.
Nodes in black lines denote the blocks that are analyzed,
those in gray lines denote the blocks not yet being analyzed, and
colored nodes denote the blocks that are currently in the worklist of the analyzer.
One can toggle whether to show the nodes in the worklist by the menu button on the top right.
When a user selects a block from the CFG, the list of the instructions in the block
and the state just before analyzing the block are displayed on the left.
